---
title: "Untitled"
author: "claire"
date: "2018年7月11日"
output: html_document
---

#Ch1
###Intro to basics

kinds of variable:
	Decimals values like 4.5 are called numerics.
	Natural numbers like 4 are called integers. Integers are also numerics.
	Boolean values (TRUE or FALSE) are called logical.
	Text (or string) values are called characters.

###Vectors
Vectors are one-dimension arrays that can hold numeric data, character data, or logical data. In other words, a vector is a simple tool to store data. 
In R, you create a vector with the combine function c()

###numeric_vector <- c(1, 2, 3)
character_vector <- c("a", "b", "c")

###names()
some_vector <- c("John Doe", "poker player")
names(some_vector) <- c("Name", "Profession")

###sum() adding function

###comparison:<,>

###choose the vector 
use[] behind the vectors,notice that
c(2, 3, 4) can be abbreviated to2:4, which generates a vector with all natural numbers from 2 up to 4.
#也可以使用挑出標籤( names() )的方式選取
poker_vector["Monday"]
	mean()
#可用來算vector裡面的元素的平均
	comparison
•	 < for less than
•	> for greater than
•	<= for less than or equal to
•	>= for greater than or equal to
•	== for equal to each other
•	!= not equal to each other
#而且可以直接比較vector裡的元素
```{r}
c(4, 5, 6) > 5
```
###selection_vector
#可以從元素裡挑出符合(TRUE)條件的元素
poker_vector[selection_vector]
R knows what to do when you pass a logical vector in square brackets: it will only select the elements that correspond to TRUE in selection_vector.



###Matrix(two-dimensional)

In R, a matrix is a collection of elements of the same data type (numeric, character, or logical) arranged into a fixed number of rows and columns. 
construct a matrix in R with the matrix()
```{r}
matrix(1:9, byrow = TRUE, nrow = 3)
```
The first argument: the collection of elements that R will arrange into the rows and columns of the matrix.
The argument ‘byrow’: ndicates that the matrix is filled by the rows. If we want the matrix to be filled by the columns, we just place byrow = FALSE
The third argument ‘nrow’: indicates that the matrix should have three rows.
#註:1:9的部分也可以換成vector

###Naming a matrix
rownames(my_matrix) <- row_names_vector
colnames(my_matrix) <- col_names_vector

###rowSums()
conveniently calculates the totals for each row of a matrix. This function creates a new vector
#加總計算出的東東是vector)
rowSums(my_matrix)

###cbind()
#可增加新的/合併columns(以vector或是metrix的型態)
big_matrix <- cbind(matrix1, matrix2, vector1 ...)

 Construct star_wars_matrix
```{r}
box_office <- c(460.998, 314.4, 290.475, 247.900, 309.306, 165.8)
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), 
                                           c("US", "non-US")))
```
 The worldwide box office figures
worldwide_vector <- rowSums(star_wars_matrix)

Bind the new variable worldwide_vector as a column to star_wars_matrix
all_wars_matrix <- cbind(star_wars_matrix,worldwide_vector)
#被加的在前

###rbind()
#可增加新的/合併rows(以vector或是metrix的型態)

###colSums()
#以column為單位加總

###Selection of matrix elements
#可用[]來選取
my_matrix[1,2] first row and second column.
my_matrix[,1] selects all elements of the first column.
#加減乘除都可用在metrix
For example, 2 * my_matrix multiplies each element of my_matrix by two



###Factor
he term factor refers to a statistical data type used to store categorical variables.  categorical variable can belong to a limited number of categories.
To create factors in R, you make use of the function factor(). 
#'factor levels’是類別的種類，例如有個fector是c(男,女,男,女)，那麼leval就是男,女。
There are two types of categorical variables: a nominal categorical variable and an ordinal categorical variable.
#Nominal:不能排順序的(老鼠，獅子，馬)
#Ordinal:可以台順序的(氣溫)

###Factor levels
#可以更換level的名字
levels(factor_vector) <- c("name1", "name2",...)

###summary().
#可以計算類別出現的次數

###Ordered factors
#使用factor()之後會使裡面的數值無法比較，這時需要add two additional arguments: ordered and levels
factor(some_vector,
       ordered = TRUE,
       levels = c("lev1", "lev2" ...))


###data frame
A data frame has the variables of a data set as columns and the observations as rows.

###head()/tail()/str()
#秀出前/後幾筆/看出結構

###build datafram
#data.fram()裡放vector

#選取資料
#方法跟metrix一樣，但有更輕鬆的方式
#planets_df[1:3,2]  變成  planets_df[1:3,"type"]
#如果要整個column的東西，也可以
#planets_df$diameter
#如果要選取TRUE的資料,用name
#planets_df[rings_vector, "name"]  (有環的行星名字)
#或是用subset()
#subset(planets_df, subset = rings)
#第二個放條件(例如subset(planets_df,diameter < 1))

###order
order()>>用vector來排: positions <- order(planets_df$diameter)
list
A list in R allows you to gather a variety of objects under one name.

###Creating a list
my_list <- list(comp1, comp2 ...)
	named list
my_list <- list(name1 = your_comp1, 
                name2 = your_comp2)
###	Select
#要用[[  ]]，也可以用$

###c()
#可用來將新資料加入list
ext_list <- c(my_list , my_val)
#前者是原先的list，後者是要加上去的東西




#Ch2
###Equality
#等於==, 不等於!= (字母比順序)，TRUE=1,FALSE=0
Equality

###AND operator(&)
#交集。

###OR operator(|)
#聯集，只有false 和 false是false

###NOT operator(!)
#如果連用兩個&&或是||就只會看第一個得比較

###Conditional Statements
If
Else
else if

if (condition) {
  expr
}


###While loop

while (condition) {
  expr
}

break statement is a control statement. When R encounters it, the while loop is abandoned completely.

###For loop

#####nchar(string)
#string的字數

#####next
#跳過符合某樣條件的物件，直接進入下一個
```{r}
primes <- c(2, 3, 5, 7, 11, 13)

# loop version 1
for (p in primes) {
  print(p)
}

# loop version 2
for (i in 1:length(primes)) {
  print(primes[i])
}
```

###length(list)
#可顯現list的長度

###paste
can bring the variables into the answer

###separate the vector 
```{r}
# Pre-defined variables
rquote <- "r's internals are irrefutably intriguing"
chars <- strsplit(rquote, split = "")[[1]]
chars
```

the way to count the number of words
```{r}
# Pre-defined variables
rquote <- "r's internals are irrefutably intriguing"
chars <- strsplit(rquote, split = "")[[1]]

# Initialize rcount
rcount <- 0

# Finish the for loop
for (char in chars) {
  if (char=="r"){
    rcount<-rcount+1
  }
  if (char=="u"){
    break
  }
}
rcount
```

###Introduction to Functions
#####black box principle

#####sd()>>Standard deviation(標準差)

#####na.rm的用法
na.rm=remove NA

if want to know how to use the function, you can type
help(sample)
```{r}
?sample
```

###args(sample)
can take a over look to  arguments of the sample()function

###trim
#trim会在首尾分别去除N个异常值，其中N=样本数量*要去除的百分比(即是trim的值)
#所以mean(a, 0.1)就会在a的首尾去除11*0.1=1个数据

###abs()
subtract function

some exsample:mean(x, trim = 0, na.rm = FALSE, ...)

build my function
```{r}
my_fun <- function(arg1, arg2) {
  body
}
```

abs(x)>> absolute values

default 
#默認
```{r}
my_fun <- function(arg1, arg2 = val2) {
  body
}
```
###Arg2 is optional argument

###install.packages():install functions

###library(),require():apply the specific functions ,like “ggplot”

###search():help to know the functions that are available to be used. 

###apply:library(c("data.table", "rjson"))



###lapply
it likes the for loop in python, which can repeate a function tiward list and data.frame .

###tolower() change big alphabet to small
lapply(list,function)
lapply(list,function,specific variable in function)

###sapply
sapply(list,function)
The lapply returns a list, while the sapply returns a vector that is a simplified version of this list

###Vapply
vapply returns a vector that is a specific simplified version of a list.
#可以指定用什麼格式簡化
sapply(list,function, kind)

###Useful Functions
abs()>>absolute value

###round()>>
#四捨五入

###rev()>> provides a reversed version of its argument.

###seq(): Generate sequences, by specifying the from, to, and by arguments.
# seq函数是产生序列用的他的用法是seq(from,to,by)或者是seq（下界，by=，length=）

###rep(): Replicate elements of vectors and lists.

###sort(): Sort a vector in ascending order. Works on numerics, but also on character strings and logicals.

###rev(): Reverse the elements in a data structures for which reversal is defined.

###str(): Display the structure of any R object.

###append(): Merge vectors or lists.

###is.*(): Check for the class of an R object.

###as.*(): Convert an R object from one class to another.

###unlist(): Flatten (possibly embedded) lists to produce a vector.


Regular Expressions

###Grepl()
^a>>start with a
a＄>>wnd with a

###grep()

###sub()/gsub()
sub() only replaces the first match, whereas gsub() replaces all matches.

sub(pattern = "Adam", replacement = "world", x=vector)


###date
Sys.date()>>show the day now

Sys.time()>>show the time now

as.Date>>Create date

%Y: 4-digit year (1982)
%y: 2-digit year (82)
%m: 2-digit month (01)
%d: 2-digit day of the month (13)
%A: weekday (Wednesday)
%a: abbreviated weekday (Wed)
%B: month (January)
%b: abbreviated month (Jan)
```{r}
# Definition of character strings representing times
str1 <- "May 23, '96 hours:23 minutes:01 seconds:45"
str2 <- "2012-3-12 14:23:08"

# Convert the strings to POSIXct objects: time1, time2
time1 <- as.POSIXct(str1, format = "%B %d, '%y hours:%H minutes:%M seconds:%S")
time2<-as.POSIXct(str2)

# Convert times to formatted strings
format(time1,"%M")
format(time2,"%I:%M %p")

```
%H: hours as a decimal number (00-23)
%I: hours as a decimal number (01-12)
%M: minutes as a decimal number
%S: seconds as a decimal number
%T: shorthand notation for the typical format %H:%M:%S
%p: AM/PM indicator
```{r}
now <- Sys.time()
now + 3600          # add an hour
now - 3600 * 24     # subtract a day
```
```{r}
birth <- as.POSIXct("1879-03-14 14:37:23")
death <- as.POSIXct("1955-04-18 03:47:12")
einstein <- death - birth
einstein
```




